Evaluating infectious disease forecasts \\ with allocation scoring rules

### 2024-02-01 alloscore_manuscript/alloscore-application-shorter.tex

% latex table generated in R 4.3.1 by xtable 1.8-4 package
% Thu Feb  1 16:28:56 2024
\begin{table}[ht]
\centering
\begin{tabular}{lrrrr}
  \hline
Model & AS & MWIS & IAS centered at 15k & IAS uniform \\ 
  \hline
CU-select & 669 & 133 & 774 & 326 \\ 
  per-capita & 865 &  & 1029 & 366 \\ 
  COVIDhub-ensemble & 873 & 159 & 1067 & 438 \\ 
  USC-SI\_kJalpha & 995 & 91 & 1216 & 1097 \\ 
  JHUAPL-Gecko & 1034 & 164 & 1141 & 418 \\ 
  MUNI-ARIMA & 1084 & 169 & 1248 & 440 \\ 
  COVIDhub-trained\_ensemble & 1089 & 169 & 1271 & 823 \\ 
  COVIDhub-baseline & 1175 & 170 & 1317 & 535 \\ 
  JHUAPL-Bucky & 1358 & 102 & 1566 & 1214 \\ 
  JHUAPL-SLPHospEns & 1540 & 129 & 1604 & 1102 \\ 
  UVA-Ensemble & 2469 & 213 & 2635 & 2494 \\ 
   \hline
\end{tabular}
\caption{For one illustrative week, a comparison of allocation scores (AS), mean weighted interval scores (MWIS), and two varieties of Integrated Allocation Scores (IAS). All metrics are shown for 10 models that made forecasts of hospital admissions for 2022-01-03. Results are sorted by AS. For all metrics, lower scores indicate better accuracy.} 
\label{tab:multi-k-scores}
\end{table}

@@

>>>>

% latex table generated in R 4.3.1 by xtable 1.8-4 package
% Thu Feb  1 16:41:23 2024
\begin{table}[ht]
\centering
\begin{tabular}{lrrrr}
  \hline
Model & AS & MWIS & IAS centered at 15k & IAS uniform \\ 
  \hline
CU-select & 669 & 133 & 774 & 326 \\ 
  per-capita & 865 &  & 1029 & 366 \\ 
  COVIDhub-ensemble & 873 & 159 & 1067 & 438 \\ 
  USC-SI\_kJalpha & 995 & 91 & 1216 & 1097 \\ 
  JHUAPL-Gecko & 1034 & 164 & 1141 & 418 \\ 
  MUNI-ARIMA & 1084 & 169 & 1248 & 440 \\ 
  COVIDhub-trained\_ensemble & 1089 & 169 & 1271 & 823 \\ 
  COVIDhub-baseline & 1175 & 170 & 1317 & 535 \\ 
  JHUAPL-Bucky & 1358 & 102 & 1566 & 1214 \\ 
  JHUAPL-SLPHospEns & 1540 & 129 & 1604 & 1102 \\ 
  UVA-Ensemble & 2469 & 213 & 2635 & 2494 \\ 
   \hline
\end{tabular}
\caption{For one illustrative week, a comparison of allocation scores (AS), mean weighted interval scores (MWIS), and two varieties of Integrated Allocation Scores (IAS). All metrics are shown for 10 models that made forecasts of hospital admissions for 2022-01-03. Results are sorted by AS. For all metrics, lower scores indicate better accuracy.} 
\label{tab:multi-k-scores}
\end{table}

@@

% latex table generated in R 4.3.1 by xtable 1.8-4 package
% Thu Feb  1 16:41:28 2024
\begin{table}[ht]
\centering
\begin{tabular}{lrr}
  \hline
model & MWIS & MAS \\ 
  \hline
COVIDhub-ensemble & 70 & 389 \\ 
  per-capita & - & 464 \\ 
  COVIDhub-trained\_ensemble & 87 & 483 \\ 
  CU-select & 81 & 502 \\ 
  JHUAPL-SLPHospEns & 67 & 526 \\ 
  COVIDhub-baseline & 93 & 594 \\ 
  JHUAPL-Bucky & 112 & 643 \\ 
  MUNI-ARIMA & 116 & 707 \\ 
  JHUAPL-Gecko & 110 & 929 \\ 
  USC-SI\_kJalpha & 155 & 1473 \\ 
   \hline
\end{tabular}
\caption{Mean weighted interval scores (MWIS) and mean allocation scores (MAS) by model across 13 weeks. For the nine models that submitted forecasts for every week from 2021-11-29 through 2022-02-21, plus a per-capita allocation, these results show the average performance of each model across all weeks. Lower scores indicate better performance, and models are sorted with the most accurate allocations at the top.} 
\label{tab:multi-week-performance-summary}
\end{table}
